\section{Projects}
\cventry{2009--}{Freelance developer}{}{}{}{
 I've been freelancing since 2009, where I started to do some web/wordpress development for clients. Since then this has been my main source of income, during my studies. Languages and technologies used: php, wordpress, mysql, swift, node.js, front-end (sass, gulp, pug, js), ruby, Java, python and Arduino code.
}
\cventry{2016}{Vega World Heritage Center}{Comissioned by Stiftelsen Vegaøyan Verdensarv}{}{}{
 Togehter with Emergence Projects AS and three other freelancers, we researched and developed a complete pre-project/concept for the new Unesco world heritage center at the Vega island. I had a main resposnibility around all tech related installations and ideas. Both concept and figuring out implementation sultions and budgets. The center is going to be built during 2017/2018.
}
\cventry{2008--}{Exhibition technician}{Employer}{City}{}{
 Worked with the Norwegian Design and Archietchture Center (and former Norsk Form), Expology AS and Kunstverker AS.
}
\cventry{2012--}{Art \& architechture projects}{Bureu Detours}{}{}{
 Since 2011 I have worked with the (mainly Denmark based) creative group Bureau Detours, and part of their Norway/Oslo fraction. Detours is a group focusing on social environments in public spaces. Through Detours I have worked on creative/art projects at the small Island Utsira in a lighthouse, Kunsthall Grenland Porsgrunn and at the art festival Lunga in Seyðisfjörður, Island---where I created a pirate radio transmitter.
}
